The DAO Hack

### 2019-01-06 paper/paper.tex

The split function has on

>>>>

The split function contains a function called withdrawRewardFor which calls rewardAccount.payOut. The first two functions are defined in the DAO code and as such can't be changed at will. The payout function however is in the attackers hands. He can do there whatever he desires. This is mostly used for logging or other custom implementations.

But only with this we can't create an attack. If the splitDAO and the withdrawRewardFor functions were implemented correctly a call to external code would be harmless. However, the splitDAO function first calls withdrawRewardFor and then sets the balance of the user to 0. With this if splitDAO gets called multiple times withdrawRewardFor will return the tokens multiple times.
